fGFPCA dynamic prediction

### 2023-01-26 f-GFPCA.Rmd
interval prediction

$$Var(\hat{\boldsymbol{\eta}}-\boldsymbol{\eta})=Var(\boldsymbol{\hat{f_0}-f_0})+\boldsymbol{\Phi\Gamma \Phi^T}+\hat{\sigma_{\epsilon}}^2$$

What happens to the variance of mean function? In practice it is estimated by smoothed population mean at each observation time.

Note:

- $\boldsymbol{\Gamma}$ is estimated from FPCA. $\hat{\boldsymbol{\xi}}$ is also derived conditional on this covariance matrix.
- <span style="color: red;"> ? Covariance of $\boldsymbol{\hat{f_0}-\eta}$ and $\hat{\boldsymbol{\xi}}$ should be 0 by assumption? </span>
- <span style="color: red;"> $Var(\boldsymbol{\hat{f_0}-f_0})$ should not change from in-sample prediction formula since it is only related to the FPCA part? </span>

$$Var(\boldsymbol{\hat{f_0}-f_0})=\boldsymbol{\Phi(H\Phi_m\Gamma)\Phi^T}$$

$$Var(\hat{\boldsymbol{\eta}}-\boldsymbol{\eta})=\boldsymbol{\Phi(H\Phi_m+I_K)\Gamma\Phi^T}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I}_m$$

>>>>

$$Var(\hat{\boldsymbol{\eta}}-\boldsymbol{\eta})=Var(\boldsymbol{\hat{f_0}-f_0})+\boldsymbol{\Phi Var(\hat{\xi}-\xi) \Phi^T}+Var(\epsilon)$$

- The three components should be mutally independent? 
- Through some derivation, I think $Var(\boldsymbol{f_0})=\frac{Var(\boldsymbol{Y})}{N} = \frac{1}{N}\boldsymbol{\Phi\Gamma \Phi}+\sigma_{\epsilon}^2\boldsymbol{I}_m$.
- Variance of $\hat{\boldsymbol{\xi}}$ will depend on the method used for its estimation
- $Var(\epsilon) =\hat{\sigma}_{\epsilon}^2$ from FPCA
- Very different approach from in-sample estimation

Additional questions:

Variance of $\boldsymbol{\xi}$ and random error is in fact given from the FPCA procedure. But we need to variance of mean function for the actual prediction interval.

What happens to the variance of mean function? In practice it is estimated by smoothed population mean at each observation time. It looks like in existing derivations, outcomes are usually assumed to be centered.
